### 2021-04-14 appendix.tex
Consistently reference extended versions.

\subsubsection*{Types}
Types ($\pcp{\ty{A}}, \pcp{\ty{B}}$) in PCP are based on classical linear logic propositions, and are defined by the following grammar:
\[
  \usingnamespace{pcp}
  \begin{array}{lcl}
    \ty{A}, \ty{B}
    & \Coloneqq & \ty{\tytens[\cs{o}]{A}{B}}
      \sep        \ty{\typarr[\cs{o}]{A}{B}}
      \sep        \ty{\tyone[\cs{o}]}
      \sep        \ty{\tybot[\cs{o}]}
      \sep        \ty{\typlus[\cs{o}]{A}{B}}
      \sep        \ty{\tywith[\cs{o}]{A}{B}}
      \sep        \ty{\tynil[\cs{o}]}
      \sep        \ty{\tytop[\cs{o}]}
  \end{array}
\]
Each connective is annotated with a priority $\cs{o}\in\mathbb{N}$.
Types $\pcp{\ty{\tytens[\cs{o}]{A}{B}}}$ and $\pcp{\ty{\typarr[\cs{o}]{A}{B}}}$ type the endpoints of a channel over which we send or receive a channel of type $\pcp{\ty{A}}$, and then proceed as type $\pcp{\ty{B}}$. Types $\pcp{\ty{\tyone[\cs{o}]}}$ and $\pcp{\ty{{\tybot}[\cs{o}]}}$ type the endpoints of a channel whose session has terminated, and over which we send or receive a \emph{ping} before closing the channel. These two types act as units for $\pcp{\ty{\tytens[\cs{o}]{A}{B}}}$ and $\pcp{\ty{\typarr[\cs{o}]{A}{B}}}$, respectively.
Types $\pcp{\ty{\typlus[\cs{o}]{A}{B}}}$ and $\pcp{\ty{\tywith[\cs{o}]{A}{B}}}$ type the endpoints of a channel over which we can receive or send a choice between two branches $\pcp{\ty{A}}$ or $\pcp{\ty{B}}$. We have opted for a simplified version of choice and followed the original Wadler's CP \cite{wadler14}, however types $\ty{\oplus}$ and $\ty{\with}$ can be trivially generalised to $\pcp{\ty{\oplus^{\cs{o}}\{l_i:A_i\}_{i\in I}}}$ and $\pcp{\ty{\with^{\cs{o}}\{l_i:A_i\}_{i\in I}}}$, respectively, as in the original PCP \cite{dardhagay18}.
Types $\pcp{\ty{\tynil[\cs{o}]}}$ and $\pcp{\ty{\tytop[\cs{o}]}}$ type the endpoints of a channel over which we can send or receive a choice between \emph{no options}. These two types act as units for $\pcp{\ty{\typlus[\cs{o}]{A}{B}}}$ and $\pcp{\ty{\tywith[\cs{o}]{A}{B}}}$, respectively.

@@

The main change we make to PCP is \emph{removing commuting conversions}. Commuting conversions are necessary if we want our reduction strategy to correspond \emph{exactly} to cut (or cycle in \cite{dardhagay18}) elimination. However, as Lindley and Morris~\cite{lindleymorris15} show, all communications that can be performed \emph{with} the use of commuting conversions, can also be performed \emph{without} them, but using structural congruence.

@@

In PCP, commuting conversions break our intuition that an action with lower priority occurs before an action with higher priority. To cite Dardha and Gay~\cite{dardhagay18} ``\emph{if a prefix on a channel endpoint $\pcp{\tm{x}}$ with priority $\cs{o}$ is pulled out at top level, then to preserve priority constraints in the typing rules [..], it is necessary to increase priorities of all actions after the prefix on $\pcp{\tm{x}}$}'' by $\cs{o+1}$.

@@

Finally, since our reduction relation is a strict subset of the reduction relation in the original~\cite{dardhagay18}, we defer to their proofs. We prove progress for our version of PCP, see~\cref{prf:thm-pcp-closed-progress}.

@@

\section{Milner's Cyclic Scheduler}
\label{sec:milner}
As an example of a deadlock-free cyclic process, Dardha and Gay~\cite{dardhagay18} introduce an implementation of Milner's cyclic scheduler~\cite{milner89} in Priority CP. We reproduce that scheduler here, and show its translation to Priority GV.

>>>>

\subsubsection*{Types}
Types ($\pcp{\ty{A}}, \pcp{\ty{B}}$) in PCP are based on classical linear logic propositions, and are defined by the following grammar:
\[
  \usingnamespace{pcp}
  \begin{array}{lcl}
    \ty{A}, \ty{B}
    & \Coloneqq & \ty{\tytens[\cs{o}]{A}{B}}
      \sep        \ty{\typarr[\cs{o}]{A}{B}}
      \sep        \ty{\tyone[\cs{o}]}
      \sep        \ty{\tybot[\cs{o}]}
      \sep        \ty{\typlus[\cs{o}]{A}{B}}
      \sep        \ty{\tywith[\cs{o}]{A}{B}}
      \sep        \ty{\tynil[\cs{o}]}
      \sep        \ty{\tytop[\cs{o}]}
  \end{array}
\]
Each connective is annotated with a priority $\cs{o}\in\mathbb{N}$.
Types $\pcp{\ty{\tytens[\cs{o}]{A}{B}}}$ and $\pcp{\ty{\typarr[\cs{o}]{A}{B}}}$ type the endpoints of a channel over which we send or receive a channel of type $\pcp{\ty{A}}$, and then proceed as type $\pcp{\ty{B}}$. Types $\pcp{\ty{\tyone[\cs{o}]}}$ and $\pcp{\ty{{\tybot}[\cs{o}]}}$ type the endpoints of a channel whose session has terminated, and over which we send or receive a \emph{ping} before closing the channel. These two types act as units for $\pcp{\ty{\tytens[\cs{o}]{A}{B}}}$ and $\pcp{\ty{\typarr[\cs{o}]{A}{B}}}$, respectively.
Types $\pcp{\ty{\typlus[\cs{o}]{A}{B}}}$ and $\pcp{\ty{\tywith[\cs{o}]{A}{B}}}$ type the endpoints of a channel over which we can receive or send a choice between two branches $\pcp{\ty{A}}$ or $\pcp{\ty{B}}$. We have opted for a simplified version of choice and followed the original Wadler's CP \cite{wadler14}, however types $\ty{\oplus}$ and $\ty{\with}$ can be trivially generalised to $\pcp{\ty{\oplus^{\cs{o}}\{l_i:A_i\}_{i\in I}}}$ and $\pcp{\ty{\with^{\cs{o}}\{l_i:A_i\}_{i\in I}}}$, respectively, as in the original PCP \cite{dardhagay18extended}.
Types $\pcp{\ty{\tynil[\cs{o}]}}$ and $\pcp{\ty{\tytop[\cs{o}]}}$ type the endpoints of a channel over which we can send or receive a choice between \emph{no options}. These two types act as units for $\pcp{\ty{\typlus[\cs{o}]{A}{B}}}$ and $\pcp{\ty{\tywith[\cs{o}]{A}{B}}}$, respectively.

@@

The main change we make to PCP is \emph{removing commuting conversions}. Commuting conversions are necessary if we want our reduction strategy to correspond \emph{exactly} to cut (or cycle in \cite{dardhagay18extended}) elimination. However, as Lindley and Morris~\cite{lindleymorris15} show, all communications that can be performed \emph{with} the use of commuting conversions, can also be performed \emph{without} them, but using structural congruence.

@@

In PCP, commuting conversions break our intuition that an action with lower priority occurs before an action with higher priority. To cite Dardha and Gay~\cite{dardhagay18extended} ``\emph{if a prefix on a channel endpoint $\pcp{\tm{x}}$ with priority $\cs{o}$ is pulled out at top level, then to preserve priority constraints in the typing rules [..], it is necessary to increase priorities of all actions after the prefix on $\pcp{\tm{x}}$}'' by $\cs{o+1}$.

@@

Finally, since our reduction relation is a strict subset of the reduction relation in the original~\cite{dardhagay18extended}, we defer to their proofs. We prove progress for our version of PCP, see~\cref{prf:thm-pcp-closed-progress}.

@@

\section{Milner's Cyclic Scheduler}
\label{sec:milner}
As an example of a deadlock-free cyclic process, Dardha and Gay~\cite{dardhagay18extended} introduce an implementation of Milner's cyclic scheduler~\cite{milner89} in Priority CP. We reproduce that scheduler here, and show its translation to Priority GV.

### 2021-04-14 conclusion.tex
Consistently reference extended versions.

\subsubsection*{Ties with logic}
The correspondence between logic and types lays the foundation for functional programming~\cite{wadler15}.
Since its inception by Girard~\cite{girard87}, linear logic has been a candidate for a foundational correspondence for concurrent programs.
A~correspondence with linear $\pi$-calculus was established early on by Abramsky~\cite{abramsky94} and Bellin and Scott~\cite{bellinscott94}. Many years later, correspondences with the $\pi$-calculus with binary session types were proposed. Caires and Pfenning~\cite{cairespfenning10} propose a correspondence with dual intuitionistic linear logic, while Wadler~\cite{wadler14} proposes a correspondence with classical linear logic. Both guarantee deadlock freedom via their connection to logic, as a consequence of cut elimination.
Dardha and Gay~\cite{dardhagay18} integrate Kobayashi and Padovani's work on priorities~\cite{kobayashi06,padovani14} with CP, loosening its ties to linear logic in exchange for expressivity.
Dardha and P\'{e}rez~\cite{dardhaperez15} compare Kobayashi-style typing and CLL typing, and show that CLL corresponds to a subsystem of Kobayashi's where restriction is applied once.
Balzer~\etal~\cite{balzerpfenning17} introduce sharing, which breaks deadlock freedom.
They later restore deadlock freedom using priorities~\cite{balzertoninho19}.
Carbone~\etal~\cite{CarboneMSY15,carbonelindley16} give a logical view of MPST with a generalised duality.
Caires and P\'{e}rez~\cite{CairesP16} give a presentation of MPST in terms of binary session types and the use of a \emph{medium process} which guarantee protocol fidelity and deadlock freedom.
Their binary session types are rooted in linear logic following the propositions-as-sessions correspondences.
Ciobanu and Horne~\cite{CiobanuH15} gave the first propositions-as-sessions correspondence of MPST with the \emph{calculus of structures}~\cite{Guglielmi07} with global and local session types are inspired by Scribble, which determines whether local session types can be combined in a deadlock free manner.
Horne~\cite{Horne20} presents a system for subtyping and multiparty compatibility where compatible processes are race free and deadlock free using a propositions-as-sessions correspondence, similar to the approach in~\cite{CiobanuH15}, with a non-commutative extension of linear logic.

\subsubsection*{Conclusion}
We answered our research question by presenting Priority GV, a~session-typed functional language which allows cyclic communication structures and uses priorities to ensure deadlock freedom. We showed its relation to Priority CP~\cite{dardhagay18} via an operational correspondence.

>>>>

\subsubsection*{Ties with logic}
The correspondence between logic and types lays the foundation for functional programming~\cite{wadler15}.
Since its inception by Girard~\cite{girard87}, linear logic has been a candidate for a foundational correspondence for concurrent programs.
A~correspondence with linear $\pi$-calculus was established early on by Abramsky~\cite{abramsky94} and Bellin and Scott~\cite{bellinscott94}. Many years later, correspondences with the $\pi$-calculus with binary session types were proposed. Caires and Pfenning~\cite{cairespfenning10} propose a correspondence with dual intuitionistic linear logic, while Wadler~\cite{wadler14} proposes a correspondence with classical linear logic. Both guarantee deadlock freedom via their connection to logic, as a consequence of cut elimination.
Dardha and Gay~\cite{dardhagay18extended} integrate Kobayashi and Padovani's work on priorities~\cite{kobayashi06,padovani14} with CP, loosening its ties to linear logic in exchange for expressivity.
Dardha and P\'{e}rez~\cite{dardhaperez15extended} compare Kobayashi-style typing and CLL typing, and show that CLL corresponds to a subsystem of Kobayashi's where restriction is applied once.
Balzer~\etal~\cite{balzerpfenning17} introduce sharing, which breaks deadlock freedom.
They later restore deadlock freedom using priorities~\cite{balzertoninho19}.
Carbone~\etal~\cite{CarboneMSY15,carbonelindley16} give a logical view of MPST with a generalised duality.
Caires and P\'{e}rez~\cite{CairesP16} give a presentation of MPST in terms of binary session types and the use of a \emph{medium process} which guarantee protocol fidelity and deadlock freedom.
Their binary session types are rooted in linear logic following the propositions-as-sessions correspondences.
Ciobanu and Horne~\cite{CiobanuH15} gave the first propositions-as-sessions correspondence of MPST with the \emph{calculus of structures}~\cite{Guglielmi07} with global and local session types are inspired by Scribble, which determines whether local session types can be combined in a deadlock free manner.
Horne~\cite{Horne20} presents a system for subtyping and multiparty compatibility where compatible processes are race free and deadlock free using a propositions-as-sessions correspondence, similar to the approach in~\cite{CiobanuH15}, with a non-commutative extension of linear logic.

\subsubsection*{Conclusion}
We answered our research question by presenting Priority GV, a~session-typed functional language which allows cyclic communication structures and uses priorities to ensure deadlock freedom. We showed its relation to Priority CP~\cite{dardhagay18extended} via an operational correspondence.

### 2021-04-14 introduction.tex
Consistently reference extended versions.

\begin{document}
\section{Introduction}
Session types~\cite{honda93,takeuchihonda94,hondavasconcelos98} are types for protocols. Regular types ensure functions are used according to their specification. Session types ensure \emph{communication channels} are used according to their protocols. Session types have been studied in many settings. For instance, in the $\pi$-calculus~\cite{honda93,takeuchihonda94,hondavasconcelos98}, a foundational calculus for communication and concurrency, and in concurrent $\lambda$-calculi~\cite{gayvasconcelos10}, including the focus of our paper: Good Variation~\cite[GV]{wadler15,lindleymorris15}.

@@

In the $\pi$-calculus literature, a growing line of work leverages the Curry-Howard correspondences between session-typed $\pi$-calculus and linear logic~\cite{girard87}: Caires and Pfenning's $\pi$DILL~\cite{cairespfenning10} corresponds to dual intuitionistic linear logic~\cite{barber96}, and Wadler's Classical Processes~\cite[CP]{wadler14} corresponds to classical linear logic~\cite[CLL]{girard87}. Both calculi guarantee deadlock freedom, which they achieve by restricting structure of processes and shared channels to \emph{trees}, by combing name restriction and parallel composition into a single construct, corresponding to the logical cut. This ensures that two processes can only communicate via exactly one series of channels, which rules out interleavings of sessions, and guarantees deadlock freedom.
There are many downsides to combining name restriction and parallel composition---lack of modularity, difficulty with typing structural congruence or with label-transition semantics, \etc---which have led to various approaches to decoupling these constructs. Hypersequent CP~\cite{MP18,kokkemontesi19popl,kokkemontesi19tlla} and Linear Compositional Choreographies~\cite{CarboneMS18} decouple them, but maintain the correspondence to CLL and allow only tree-structured processes. Priority CP~\cite[PCP]{dardhagay18} weakens the correspondence to CLL in exchange for a more expressive language which allows cyclic-structured processes. PCP decouples CP's cut rule into two separate constructs: one for parallel composition via a mix rule, and one for name restriction via a cycle rule. To restore deadlock freedom, PCP uses \emph{priorities}~\cite{kobayashi06,padovani14}. Priorities encode the \emph{order of actions} and rule out bad interleavings. Dardha and Gay~\cite{dardhagay18} prove cycle-elimination for PCP, adapting the cut-elimination proof for classical linear logic, and deadlock freedom follows as a corollary.

@@

We follow the line of work from CP to Priority CP, and present Priority GV (PGV), a~variant of GV which decouples channel creation from thread spawning, thus allowing cyclic-structured processes, but which nonetheless guarantees deadlock freedom via priorities. This closes the circle of the connection between CP and GV~\cite{wadler14}, and their priority-based versions, PCP~\cite{dardhagay18} and PGV.
We make the following main contributions:
\begin{enumerate}[labelindent=0pt,labelwidth=1.333\parindent,align=left,labelsep*=0pt,leftmargin=!]
\item[(\secref{sec:pgv})] \textbf{Priority GV}. We present Priority GV (\secref{sec:pgv}, PGV), a session-typed functional language with priorities, and prove subject reduction (\cref{thm:pgv-subject-reduction-confs}) and progress (\cref{thm:pgv-closed-progress-confs}). We addresses several problems in the original GV language, most notably:
  \begin{enumerate*}
  \item PGV does not require the pseudo-type $S^\sharp$; and
  \item its structural congruence is type preserving.
  \end{enumerate*}
  PGV answers our research question positively as it allows cyclic-structured binary session-typed processes that are deadlock free.
\item[(\secref{sec:pcp})] \textbf{Translation from PCP to PGV}.
  We present a \emph{sound and complete encoding} of Priority CP~\cite{dardhagay18} in PGV (\secref{sec:pcp}). We prove the encoding preserves typing (\cref{thm:pcp-to-pgv-confs-preservation}) and satisfies operational correspondence (\cref{thm:pcp-to-pgv-operational-correspondence-soundness,thm:pcp-to-pgv-operational-correspondence-completeness}).
  To obtain a tight correspondence, we update PCP, moving away from commuting conversions and reduction as cut elimination towards reduction based on structural congruence, as it is standard in process calculi.
\end{enumerate}
\end{document}

>>>>

\begin{document}
\section{Introduction}
Session types~\cite{honda93,takeuchihonda94,hondavasconcelos98} are types for protocols. Regular types ensure functions are used according to their specification. Session types ensure \emph{communication channels} are used according to their protocols. Session types have been studied in many settings. For instance, in the $\pi$-calculus~\cite{honda93,takeuchihonda94,hondavasconcelos98}, a foundational calculus for communication and concurrency, and in concurrent $\lambda$-calculi~\cite{gayvasconcelos12}, including the focus of our paper: Good Variation~\cite[GV]{wadler15,lindleymorris15}.

@@

In the $\pi$-calculus literature, a growing line of work leverages the Curry-Howard correspondences between session-typed $\pi$-calculus and linear logic~\cite{girard87}: Caires and Pfenning's $\pi$DILL~\cite{cairespfenning10} corresponds to dual intuitionistic linear logic~\cite{barber96}, and Wadler's Classical Processes~\cite[CP]{wadler14} corresponds to classical linear logic~\cite[CLL]{girard87}. Both calculi guarantee deadlock freedom, which they achieve by restricting structure of processes and shared channels to \emph{trees}, by combing name restriction and parallel composition into a single construct, corresponding to the logical cut. This ensures that two processes can only communicate via exactly one series of channels, which rules out interleavings of sessions, and guarantees deadlock freedom.
There are many downsides to combining name restriction and parallel composition---lack of modularity, difficulty with typing structural congruence or with label-transition semantics, \etc---which have led to various approaches to decoupling these constructs. Hypersequent CP~\cite{MP18,kokkemontesi19popl,kokkemontesi19tlla} and Linear Compositional Choreographies~\cite{CarboneMS18} decouple them, but maintain the correspondence to CLL and allow only tree-structured processes. Priority CP~\cite[PCP]{dardhagay18extended} weakens the correspondence to CLL in exchange for a more expressive language which allows cyclic-structured processes. PCP decouples CP's cut rule into two separate constructs: one for parallel composition via a mix rule, and one for name restriction via a cycle rule. To restore deadlock freedom, PCP uses \emph{priorities}~\cite{kobayashi06,padovani14}. Priorities encode the \emph{order of actions} and rule out bad interleavings. Dardha and Gay~\cite{dardhagay18extended} prove cycle-elimination for PCP, adapting the cut-elimination proof for classical linear logic, and deadlock freedom follows as a corollary.

@@

We follow the line of work from CP to Priority CP, and present Priority GV (PGV), a~variant of GV which decouples channel creation from thread spawning, thus allowing cyclic-structured processes, but which nonetheless guarantees deadlock freedom via priorities. This closes the circle of the connection between CP and GV~\cite{wadler14}, and their priority-based versions, PCP~\cite{dardhagay18extended} and PGV.
We make the following main contributions:
\begin{enumerate}[labelindent=0pt,labelwidth=1.333\parindent,align=left,labelsep*=0pt,leftmargin=!]
\item[(\secref{sec:pgv})] \textbf{Priority GV}. We present Priority GV (\secref{sec:pgv}, PGV), a session-typed functional language with priorities, and prove subject reduction (\cref{thm:pgv-subject-reduction-confs}) and progress (\cref{thm:pgv-closed-progress-confs}). We addresses several problems in the original GV language, most notably:
  \begin{enumerate*}
  \item PGV does not require the pseudo-type $S^\sharp$; and
  \item its structural congruence is type preserving.
  \end{enumerate*}
  PGV answers our research question positively as it allows cyclic-structured binary session-typed processes that are deadlock free.
\item[(\secref{sec:pcp})] \textbf{Translation from PCP to PGV}.
  We present a \emph{sound and complete encoding} of Priority CP~\cite{dardhagay18extended} in PGV (\secref{sec:pcp}). We prove the encoding preserves typing (\cref{thm:pcp-to-pgv-confs-preservation}) and satisfies operational correspondence (\cref{thm:pcp-to-pgv-operational-correspondence-soundness,thm:pcp-to-pgv-operational-correspondence-completeness}).
  To obtain a tight correspondence, we update PCP, moving away from commuting conversions and reduction as cut elimination towards reduction based on structural congruence, as it is standard in process calculi.
\end{enumerate}
\end{document}

### 2021-04-14 priority-cp.tex
Consistently reference extended versions.

We present a correspondence between Priority GV and an updated version of Priority CP~\cite[PCP]{dardhagay18}, which is Wadler's CP~\cite{wadler14} with priorities. This correspondence connects PGV to (a~relaxed variant of) classical linear logic.

@@

PCP decomposes cut into \LabTirName{T-Res} and \LabTirName{T-Par} rules---logically corresponding to cycle and mix rules, respectively---and guarantees deadlock freedom by using priority constraints, \eg, as in \LabTirName{T-Send}. The full typing rules and operational semantics are available in \cref{fig:pcp-operational-semantics,fig:pcp-typing} in \cref{app:revisiting-PCP}:
\begin{mathpar}
  \small
  \inferrule*[lab=T-Res]{
    \seq{P}{\ty{\Gamma},\tmty{x}{A},\tmty{y}{\co{A}}}
  }{\seq{\res{x}{y}{P}}{\ty{\Gamma}}}
  \inferrule*[lab=T-Par]{
    \seq{P}{\ty{\Gamma}}
    \and
    \seq{Q}{\ty{\Delta}}
  }{\seq{\ppar{P}{Q}}{\ty{\Gamma},\ty{\Delta}}}
  \inferrule*[lab=T-Send]{
    \seq{P}{\ty{\Gamma},\tmty{y}{A},\tmty{x}{B}}
    \and
    \cs{o}<\minpr(\ty{\Gamma},\ty{A},\ty{B})
  }{\seq{\send{x}{y}{P}}{\ty{\Gamma},\tmty{x}{\tytens[\cs{o}]{A}{B}}}}
\end{mathpar}

The main change we make to PCP is \emph{removing commuting conversions} and defining an operational semantics based on structural congruence. Commuting conversions are necessary if we want our reduction strategy to correspond \emph{exactly} to cut elimination.
However, from the perspective of process calculi, commuting conversions behave strangely: they allow an input/output action to be moved to the top of a process, thus potentially blocking actions which were previously possible (an example is given in \cref{app:commuting-conversions}). This makes CP, and Dardha and Gay's PCP~\cite{dardhagay18}, non-confluent.
As Lindley and Morris~\cite{lindleymorris15} show, all communications that can be performed \emph{with} the use of commuting conversions, can also be performed \emph{without} them, if using structural congruence.
%Consider the commuting conversion $(\kappa_{\parr})$ for $\pcp{\tm{\recv{x}{y}{P}}}$:
%\begin{mathpar}
%  (\kappa_{\parr})
%  \quad
%  \tm{\res{z}{z'}{(\ppar{\recv{x}{y}{P}}{Q})}}
%  \red
%  \tm{\recv{x}{y}{\res{z}{z'}{(\ppar{P}{Q})}}}
%\end{mathpar}
%As a result of $(\kappa_{\parr})$, $\pcp{\tm{Q}}$ becomes blocked on $\pcp{\tm{\labrecv{x}{y}}}$, and any actions $\pcp{\tm{Q}}$ was able to perform become unavailable. Consequently, CP is non-confluent:
%\begin{mathpar}
%  \setlength{\arraycolsep}{2em}
%  \begin{array}{cc}
%    \multicolumn{2}{c}{%
%    \hspace*{10ex}
%    {\tm{\res{x}{x'}{(\ppar{\recv{a}{y}{P}}{\res{z}{z'}{(\ppar{\close{z}{\halt}}{\wait{z'}{Q}})}})}}}}
%    \\
%    \qquad\rotatebox[origin=c]{270}{$\red\hphantom{{}^+}$}
%    &
%    \rotatebox[origin=c]{270}{$\red^+$}\qquad
%    \\
%    {\tm{\recv{a}{y}{\res{x}{x'}{(\ppar{P}{\res{z}{z'}{(\ppar{\close{z}{\halt}}{\wait{z'}{Q}})}})}}}}
%    &
%    {\tm{\recv{a}{y}{\res{x}{x'}{(\ppar{P}{Q})}}}}
%  \end{array}
%\end{mathpar}
%

In  particular for PCP, commuting conversions break our intuition that an action with lower priority \emph{occurs before} an action with higher priority. To cite Dardha and Gay~\cite{dardhagay18} ``\emph{if a prefix on a channel endpoint $\pcp{\tm{x}}$ with priority $\cs{o}$ is pulled out at top level, then to preserve priority constraints in the typing rules [..], it is necessary to increase priorities of all actions after the prefix on $\pcp{\tm{x}}$}'' by $\cs{o+1}$.
One benefit of removing commuting conversions is that we no longer need to dynamically change the priorities during reduction, which means that the intuition for priorities holds true in our updated version of PCP. Furthermore, we can safely define reduction on untyped processes, which means that type and priority information is erasable!

>>>>

We present a correspondence between Priority GV and an updated version of Priority CP~\cite[PCP]{dardhagay18extended}, which is Wadler's CP~\cite{wadler14} with priorities. This correspondence connects PGV to (a~relaxed variant of) classical linear logic.

@@

PCP decomposes cut into \LabTirName{T-Res} and \LabTirName{T-Par} rules---corresponding to cycle and mix rules, respectively---and guarantees deadlock freedom by using priority constraints, \eg, as in \LabTirName{T-Send}. % The full typing rules and operational semantics are available in \cref{fig:pcp-operational-semantics,fig:pcp-typing} in \cref{app:revisiting-PCP}:
\begin{mathpar}
  \small
  \inferrule*[lab=T-Res]{
    \seq{P}{\ty{\Gamma},\tmty{x}{A},\tmty{y}{\co{A}}}
  }{\seq{\res{x}{y}{P}}{\ty{\Gamma}}}
  \inferrule*[lab=T-Par]{
    \seq{P}{\ty{\Gamma}}
    \and
    \seq{Q}{\ty{\Delta}}
  }{\seq{\ppar{P}{Q}}{\ty{\Gamma},\ty{\Delta}}}
  \inferrule*[lab=T-Send]{
    \seq{P}{\ty{\Gamma},\tmty{y}{A},\tmty{x}{B}}
    \and
    \cs{o}<\minpr(\ty{\Gamma},\ty{A},\ty{B})
  }{\seq{\send{x}{y}{P}}{\ty{\Gamma},\tmty{x}{\tytens[\cs{o}]{A}{B}}}}
\end{mathpar}

The main change we make to PCP is \emph{removing commuting conversions} and defining an operational semantics based on structural congruence. Commuting conversions are necessary if we want our reduction strategy to correspond \emph{exactly} to cut elimination.
However, from the perspective of process calculi, commuting conversions behave strangely: they allow an input/output action to be moved to the top of a process, thus potentially blocking actions which were previously possible. This makes CP, and Dardha and Gay's PCP~\cite{dardhagay18extended}, non-confluent.
As Lindley and Morris~\cite{lindleymorris15} show, all communications that can be performed \emph{with} the use of commuting conversions, can also be performed \emph{without} them, using structural congruence.

%Consider the commuting conversion $(\kappa_{\parr})$ for $\pcp{\tm{\recv{x}{y}{P}}}$:
%\begin{mathpar}
%  (\kappa_{\parr})
%  \quad
%  \tm{\res{z}{z'}{(\ppar{\recv{x}{y}{P}}{Q})}}
%  \red
%  \tm{\recv{x}{y}{\res{z}{z'}{(\ppar{P}{Q})}}}
%\end{mathpar}
%As a result of $(\kappa_{\parr})$, $\pcp{\tm{Q}}$ becomes blocked on $\pcp{\tm{\labrecv{x}{y}}}$, and any actions $\pcp{\tm{Q}}$ was able to perform become unavailable. Consequently, CP is non-confluent:
%\begin{mathpar}
%  \setlength{\arraycolsep}{2em}
%  \begin{array}{cc}
%    \multicolumn{2}{c}{%
%    \hspace*{10ex}
%    {\tm{\res{x}{x'}{(\ppar{\recv{a}{y}{P}}{\res{z}{z'}{(\ppar{\close{z}{\halt}}{\wait{z'}{Q}})}})}}}}
%    \\
%    \qquad\rotatebox[origin=c]{270}{$\red\hphantom{{}^+}$}
%    &
%    \rotatebox[origin=c]{270}{$\red^+$}\qquad
%    \\
%    {\tm{\recv{a}{y}{\res{x}{x'}{(\ppar{P}{\res{z}{z'}{(\ppar{\close{z}{\halt}}{\wait{z'}{Q}})}})}}}}
%    &
%    {\tm{\recv{a}{y}{\res{x}{x'}{(\ppar{P}{Q})}}}}
%  \end{array}
%\end{mathpar}

In  particular for PCP, commuting conversions break our intuition that an action with lower priority \emph{occurs before} an action with higher priority. To cite Dardha and Gay~\cite{dardhagay18extended} ``\emph{if a prefix on a channel endpoint $\pcp{\tm{x}}$ with priority $\cs{o}$ is pulled out at top level, then to preserve priority constraints in the typing rules [..], it is necessary to increase priorities of all actions after the prefix on $\pcp{\tm{x}}$}'' by $\cs{o+1}$.
One benefit of removing commuting conversions is that we no longer need to dynamically change the priorities during reduction, which means that the intuition for priorities holds true in our updated version of PCP. Furthermore, we can safely define reduction on untyped processes, which means that type and priority information is erasable!
